---
title: "Assignment 3 FML"
author: "Chaitanya"
date: "2022-10-26"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## \-\--

#Importing the Dataset

```{r}
library(readr)
UniversalBank <- read_csv("~/UniversalBank.csv")
View(UniversalBank)

```

#calling Libraries

```{r}
library(caret)

library(class)

library(ISLR)

```

#Converting Personal.loan Variable

```{r}
UniversalBank$`Personal Loan`=as.factor(UniversalBank$`Personal Loan`)
summary(UniversalBank)
```

#Converting Online Variable

```{r}
UniversalBank$Online = as.factor(UniversalBank$Online) 

summary(UniversalBank$Online)
```

#Converting Creditcard Variable

```{r}
UniversalBank$CreditCard = as.factor(UniversalBank$CreditCard) 
summary(UniversalBank)

UniversalBank$Online<-as.factor(UniversalBank$Online)
is.factor(UniversalBank$Online)
UniversalBank$CreditCard<-as.factor(UniversalBank$CreditCard)
is.factor(UniversalBank$CreditCard)
str(UniversalBank)


```

#Task_1

#Data Partition

```{r}
set.seed(64064)
library(caret)
Train_Index = createDataPartition(UniversalBank$`Personal Loan`,p=0.60, list = FALSE) # 60% reserved for Train
Train.df=UniversalBank[Train_Index,]
Validation.df=UniversalBank[-Train_Index,]

```


```{r}

mytable<- xtabs(~CreditCard+Online+`Personal Loan`, data = Train.df)


ftable(mytable)

```

#Task_B:what is the probability that this customer will accept the loan offer? [This is the probability of loan acceptance (Loan = 1) conditional on having a bank credit card (CC = 1) and being an active user of online banking services (Online = 1)]

```{r}
Probability = 59/(479+59)

Probability

```

#Task_C:

#pivot table with Personal loan as row and credit card as column using training data.

```{r}
table(CreditCard=Train.df$CreditCard, `Personal Loan`=Train.df$`Personal Loan`)


```

#pivot table with Personal loan as row and Online as column using training data.

```{r}
table(Online=Train.df$Online, `Personal Loan`=Train.df$`Personal Loan`)


```

#pivot table for Personal loan

```{r}
table(`Personal Loan`=Train.df$`Personal Loan`, CreditCard=Train.df$CreditCard)
```

#Task_D:

#i.P(CC = 1 \| Loan = 1)(the proportion of credit card holders among the loan acceptors)

```{r}
Probability_6 = 93/(195+93)

Probability_6

```

#ii.P(Online = 1 \| Loan = 1)

```{r}
Probability_7 = 179/(109+179)

Probability_7

```

#iii.P(Loan = 1) (the proportion of loan acceptors)

```{r}
Probability_8 = 288/(2712+288)

Probability_8

```

#iv.P(CC = 1 \| Loan = 0)

```{r}
Probability_9 = 788/(1924+788)

Probability_9

```

#v.P(Online = 1 \| Loan = 0)

```{r}
Probability_10 = 1631/(1631+1081)

Probability_10
```

#vi.P(Loan = 0)

```{r}
Probability_11 = 2712/(2712+288)

Probability_11
```

#Task_E:

#P(Loan = 1 \| CC = 1, Online = 1).

```{r}
naive_Bayes_probability <- (Probability_6*Probability_7*Probability_8) / 

                          ((Probability_6*Probability_7*Probability_8) + 

                             (Probability_9*Probability_10*Probability_11))


naive_Bayes_probability
```

#Task_F:Compare this value with the one obtained from the pivot table in (B).

#Which is a more accurate estimate?

```{r}
#0.1087106 in task-E is very similar to the  0.1096654 in task-B.

#The difference between the exact and naive bayes methods is that

#the exact approach requires the same independent variable classifications to predict, 

#whereas the naive bayes method does not.



```

#Task_G:

\# P(Loan = 1 \| CC = 1, Online = 1)

#Run naive Bayes on the data. Examine the model output on training data, and find the entry

#that corresponds to P(Loan = 1 \| CC = 1, Online = 1). Compare this to the number you

#obtained in (E).

```{r}
library(e1071)

```

```{r}

library(naivebayes)
library(mlbench)
nb.model<- naiveBayes(`Personal Loan`~Online+CreditCard, data= Train.df)

To_Predict=data.frame(Online= '1', CreditCard= '1')

predict(nb.model,To_Predict,type='raw')


```

#The task-G value of 0.1087106 and the task-E value of 0.1087106 are identical.

#As a result, the naive bayes produces the same results as the prior approaches.

